\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Nakul}{Gupta}{ 
https://guptanakul.com | nakulgupta1042@gmail.com || Github: \href{https://github.com/gnakul2001} https://github.com/gnakul2001 \\
+91 77019 83886 | Delhi, India | LinkedIn: \href{https://www.linkedin.com/in/thenakulgupta/} https://www.linkedin.com/in/thenakulgupta
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.4\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming:}
\sectionsep
\textbf{Languages:}\\
\textbullet{} Proficient: Flutter, \textbf{PHP}, \textbf{C++}, MySQL\\
\textbullet{} Experienced: Java, JavaScript,\\ \hspace{\topsep}\textbf{Data Structure and Algorithm (DSA)}\\
\textbullet{} Basic: Python\\

\textbf{Tools:}\\
\textbullet{} Git \textbullet{} Linux\\

\textbf{Frameworks \& Library:} \\
\textbullet{} Proficient: \textbf{NodeJS}, Laravel \\
\textbullet{} Basic: ReactJS \\

\textbf{AWS:}\\
EC2 
\textbullet{} RDS 
\textbullet{} Route 53 
\textbullet{} Certificate Manager 
\textbullet{} S3 
\textbullet{} CloudFront 
\textbullet{} Lambda 
\textbullet{} SES 
\textbullet{} SNS \\


\subsection{Others:}
\sectionsep
Teamwork \textbullet{} Problem-solving \textbullet{} Time Management\\ Communication \textbullet{} Dependability \textbullet{} Critical thinking
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
% \sectionsep
% \subsection{University of Michigan (Coursera)}
% \descript{Programming for Everybody \\(Getting Started with Python)}
% \location{Apr 2021 - Apr 2021}
% \sectionsep

\subsection{Tecnia Institute Of Advanced Studies}
\descript{Bachelor of Computer Application}
\location{Aug 2020 - June 2023 | Delhi, India}
Class Representative (3 Years) of Batch\\
Head Student Coordinator of TechnoVision Event 2022\\
Fitness Club Coordinator (2.5 Years)\\
Eco Club Coordinator (2 Years)\\
\location{CGPA: 3.6 / 4.0}
\sectionsep

\subsection{Jain Bharati Mrigavati Vidyalaya}
\descript{Commerce with IP}
\location{Grad. May 2020 | Cum. Per 67.5\%}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}

% \subsection{Undergraduate}
% Flutter Banking App\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
% \section{Links} 
% Github:// \href{https://github.com/gnakul2001}{\bf gnakul2001} \\
% Website://  \href{https://guptanakul.com}{\bf guptanakul.com} \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}

\textbf{Google IT Automation with Python} - Google\\
\textbf{Aadhaar Hackathon 2021} - Unique Identification Authority of India (UIDAI)\\
\textbf{National Level Coding Competition} - Coding Blocks\\
\textbf{Learning Google Flutter for Mobile Developers} - LinkedIn\\
\textbf{Java 8 Essential Training} - LinkedIn\\
\textbf{Data Science} - CETPA Infotech Pvt. ltd.\\
\textbf{Advanced PHP} - LinkedIn\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.55\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\subsection{Q1 Business Solutions}
\sectionsep
\begin{tightemize}
\item Senior Product Developer (1 Year Full-Time)
\end{tightemize}
\hspace{\topsep}\location{Jun 2022 - Apr 2023}

\begin{tightemize}
\item Flutter And Web Developer (2 months Part-time)
\end{tightemize}
\hspace{\topsep}\location{May 2022 - Jun 2022}
\location{Doha, Qatar}
\begin{enumerate}
\item Developed the Admin Panel, Web App, Blogging system by which sales increases by 2.5x.
\item Improved and optimised all the APIs which makes our app 70\% faster and reduced 20\% clicks for tasks.
\item Managed 2 employees team and made hierarchy under them with 5 employees.
\item Managed CI/CD with 300+ commits and 100+ merge requests.
\item Managed all AWS activities within the company.
\end{enumerate}
\sectionsep

% \runsubsection{The Sparks Foundation}
% \descript{| Campus Ambassador Intern (3 months Internship) }
% \location{Jun 2022 - Aug 2022 | Delhi, India}
% \sectionsep

% \runsubsection{Tecnia Institute of Advanced Studies}

% \begin{tightemize}
% \item Class Representative (2+ Years)
% \end{tightemize}
% \hspace{\topsep}\location{Jan 2021 – Present}

% \begin{tightemize}
% \item Fitness Club Coordinator (1.5+ Years)
% \end{tightemize}
% \hspace{\topsep}\location{May 2021 - Present}

% \begin{tightemize}
% \item Eco Club Coordinator (1+ Years)
% \end{tightemize}
% \hspace{\topsep}\location{Jul 2021 – Present}

% \begin{tightemize}
% \item Head Student Coordinator of TechnoVision Event 2022 (1 Month - Full Event)
% \end{tightemize}
% \hspace{\topsep}\location{Feb 2022 - Feb 2022}

% \location{Delhi, India}
% \sectionsep

\runsubsection{The Sparks Foundation}
\descript{| Campus Ambassador Intern (3 months Internship) }
\location{Jun 2022 - Aug 2022 | Delhi, India}
\begin{enumerate}
\item Built a network of students of same interest.
\item Promoted the services to the students.
\end{enumerate}
\sectionsep

% \runsubsection{ClearExam}
% \descript{| IT Operation Intern (2 months Internship) }
% \location{Apr 2022 - May 2022 | Delhi, India}
% \sectionsep

\runsubsection{}
\runsubsection{Oyester Training}
\descript{| Full Stack Developer (3 months Internship) }
\location{Jun 2022 - Aug 2022 | Delhi, India}

% \begin{tightemize}
% \item Web Developer (1 month Internship)
% \end{tightemize}
% \hspace{\topsep}\location{Jun 2020 - Jun 2020}
\location{Delhi, India}
\begin{enumerate}
\item Worked on developing minor and major projects.
\item Worked in a team.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\subsection{TelePayGate (Payment Gateway) | PHP | Laravel | Bootstrap | MySQL | JavaScript | HTML | CSS}
\sectionsep
\vspace{\topsep}
\begin{tightemize}
\item Developed a payment gateway Solution to accept consumer payments, and optimize employees/merchant payouts.
\item Link: \href{https://telepaygate.guptanakul.com}{\bf telepaygate.guptanakul.com}
\end{tightemize}
\sectionsep
\sectionsep
\subsection{Covid Vaccine Finder | Python | Bootstrap | JavaScript | HTML | CSS}
\sectionsep
\vspace{\topsep}
\begin{tightemize}
\item Developed a project to find the covid vaccine near to the postcode within a certain range.
\item Link: \href{https://covid-vaccine-finder.guptanakul.com}{\bf covid-vaccine-finder.guptanakul.com}
\end{tightemize}
\sectionsep

\end{minipage} 
\sectionsep
\end{document}  \documentclass[]{article}
